---
title: "Mapping the Coronavirus Outbreak"
author: ""
date: "`r Sys.Date()`"
output: 
  html_document
---

```{r set-up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

# Getting started

1. Clone your repo `appex04-[github_name]` to create a new project
   in RStudio Cloud under the STA 199 class space.

2. Configure git
      ```{r config-git-ex, eval=FALSE}
      library(usethis)
      use_git_config(user.name="your name", user.email="your email")
      ```

# Packages and Data

We'll make use of the following packages.

```{r load-packages}
library(sf)
library(tidyverse)
```

There are two data files we will use: `world.shp`, `coronavirus.shp`. We'll
read each of these in with function `st_read()` and save them as `world` and
`virus`.

```{r}
world <- st_read("data/world.shp", quiet = TRUE)
virus <- st_read("data/coronavirus.shp", quiet = TRUE)
```

## Part 1

Take a look at objects `world` and `virus`. How many fields exist for each
object? What type of geometry is associated with each `sf` object?

```{r part-1-world}
world
```

```{r part-1-virus}
virus
```

## Part 2

Use object `world` to create a world map of the countries. You'll want to use
functions `ggplot()`, specifying the `world` dataset, and `geom_sf()` to tell 
`ggplot()` which geometry to use.

```{r part-2-p1}

```

Build on your previous map so that the countries have a fill color 
associated with the population estimate (hint: what variable would we map to the
`fill` aesthetic?). Note that variable `pop_est` is in millions. Be sure to 
label your map.

```{r part-2-p2}

```

## Part 3

Filter `world` for the country "China". Save the result as `china`. Remember
that we can use a function from the `dplyr` package to do so, utilizing pipes.

```{r part-3-china}

```

Next, we'll filter object `virus` for confirmed cases in China and save the
result as `china_cv`. The code is given below.

```{r part-3-china-cv}
china_cv <- virus %>% 
  filter(cntry_r == "Mainland China", !is.na(confrmd))
```


## Part 4

Use the template provided to overlay the point locations of the coronavirus
in China with a map of China. Have the size of the points reflect the
number of confirmed cases. Refer to slides 29 and 30 as a guide.

```{r part-4, fig.width=9, fig.height=6}
# UNCOMMENT ME WHEN YOU'RE READY TO DO THIS EXERCISE!

# ggplot(data = china) +
#   geom_sf(fill = "#DE2910")
```

*Hints and additional instructions:*

- you will have to add another `geom_sf()` layer with the appropriate object for
the coronavirus cases
- inside this additional `geom_sf()`, set point colors as `color = "#FFDE00"`, 
and include `show.legend = "point"` to show the legend as points rather than
squares.


```{r fig.width=9, fig.height=6}

```

# Submission

## Stage, commit and push

1. Stage your modified files.
2. Commit your changes with an informative message.
3. Push your changes to your GitHub repo.
4. Verify your files were updated on GitHub.

# Slide notes

# References

1. Simple Features for R vignette, https://r-spatial.github.io/sf/
